Data Dashboard

### 2020-05-13 analysis/05_market_simulator.Rmd

```{r load data}
intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))
#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donars         -0.376
#   11. Government Grants            -0.252
#   12. Critized by Government       -0.663
#   13. Under Government Crackdown   -1.011

@@

@@

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

@@

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
             geom_col() +
             labs(x="") + 
             #scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
             theme(legend.position = "none", axis.text.x = element_text(angle = 10, hjust = 1)) +
             facet_wrap(~Type)
    )
})
```

@@

```{r}
renderValueBox({
  choice = df()
  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(gp_exp_util,
           color = "#3fad48")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(ox_exp_util,
           color = "#006633")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(rc_exp_util,
           color = "#660000")
})
```

@@

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)

>>>>

```{r load data}
charity_voluntarism <- readRDS(here('analysis', 'output', 'posterior_draws', 'charity_voluntarism.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

demographics <- readRDS(here('analysis', 'output', 'posterior_draws', 'demographics.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

intercept_centered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_centered.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

intercept_conjugate <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_conjugate.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Gamma))

intercept_noncentered <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

political_ideology <- readRDS(here('analysis', 'output', 'posterior_draws', 'political_ideology.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

public_affairs <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_affairs.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

public_political <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

public_political_social <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

public_political_social_charity <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

social_views <- readRDS(here('analysis', 'output', 'posterior_draws', 'social_views.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))

#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donars         -0.376
#   11. Government Grants            -0.252
#   12. Critized by Government       -0.663
#   13. Under Government Crackdown   -1.011

@@

Inputs {.sidebar}
-------------------------------------------------------

```{r echo=FALSE}
selectInput("model_choice", 
            label = "Select Model:",
            choices = c("charity_voluntarism",
                        "demographics",
                        "intercept_centered",
                        "intercept_conjugate",
                        "intercept_noncentered",
                        "political_ideology",
                        "public_affairs",
                        "public_political",
                        "public_political_social",
                        "public_political_social_charity",
                        "public_political_social_charity_demo",
                        "social_views"))

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {

    selectInput("charity_importance", 
              label = "Charity Importance:",
              choices = c("0", '1', '2', '3','4','5','6','7'))
  }
})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
  selectInput("trust_in_charity", 
              label = "Charity Trust:",
              choices = c("0", '1', '2', '3','4','5','6','7'))
  }
})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("donation_frequency", 
               label = "Donation Frequency:",
               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
  }
})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("donation_amount", 
               label = "Donation Amount:",
               choices = c("$1-$49", '$50-$99', '$100-$499', '$500-$999','$1,000-$4,999','$5,000-$9,999','$10,000+'))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("volunteer_12", 
               label = "Volunteered in last 12 Months:",
               choices = c("Yes", "No"))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("volunteer_frequency", 
               label = "Volunteer Frequency:",
               choices = c('Once a week', 'Once a Month', 'Once every three months', 'Once every six months', 'Once a year', 'Once every few years', 'Never'))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("personal_activism", 
               label = "Personal Activism:",
               choices = c('Extremely involved', 
               'Very involved', 
               'Moderately involved', 
               'Slightly involved',
               'Never involved'))
}})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("family_activism", 
               label = "Family Activism:",
               choices = c('Extremely involved', 
               'Very involved', 
               'Moderately involved', 
               'Slightly involved',
               'Never involved'))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religious_member", 
               label = "Church Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("sport_member", 
               label = "Sport or Recreational Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("art_member", 
               label = "Art, Music, or Educational Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("labor_member", 
               label = "Labor Union Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("political_member", 
               label = "Political Party Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("environmental_member", 
               label = "Enviornmental Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("professional_member", 
               label = "Professional Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})
renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("humanitarian_member", 
               label = "Humanitarian Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("consumer_member", 
               label = "Consumer Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religious_member", 
               label = "Church Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))

  }})

renderUI({
  if (input$model_choice %in% c("charity_voluntarism", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("other_member", 
               label = "Other Org. Membership:",
               choices = c('Active Member', 
               'Inactive Member', 
               "Don't belong"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("national_news", 
               label = "Follow national news:",
               choices = c('Multiple times a day', 
               'Every day', 
               "Once a week",
               "Hardly ever",
               "Never"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("international_news", 
               label = "Follow international news:",
               choices = c('Always',
                           "Sometimes",
                           "Never"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("news_medium", 
               label = "Medium to follow news:",
               choices = c('TV', 
               'Print', 
               "Online",
               "Social Media",
               "Radio",
               "Email newsletters",
               "News app"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("international_news", 
               label = "Follow international news:",
               choices = c('Multiple times a day', 
               'Every day', 
               "Once a week",
               "Hardly ever",
               "Never"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("follow_gov", 
               label = "Follow government & public affairs:",
               choices = c('Most of the time', 
               'Some of the time', 
               "Only now and then",
               "Hardly at all"))
  }})

renderUI({
  if (input$model_choice %in% c("public_affairs", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("travel_developing", 
               label = "Travel to developing country:",
               choices = c('Yes', 
               'No'))
  }})

renderUI({
  if (input$model_choice %in% c("political_ideology", "public_political", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("polical_pref", 
               label = "Polical views from liberal to conservative:",
               choices = c('0', 
               '1', 
               "2",
               "3",
               "4",
               "5",
               "6",
               "7"))
  }})

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("institution_trust", 
               label = "Political institution trust from none to complete:",
               choices = c('0', 
               '1', 
               "2",
               "3",
               "4",
               "5",
               "6",
               "7"))
  }})

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("others_charitable", 
               label = "People should be more charitable:",
               choices = c('0', 
               '1', 
               "2",
               "3",
               "4",
               "5",
               "6",
               "7"))
  }}) #??

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("worship_attendance", 
               label = "Worship service attendance:",
               choices = c('Multiple times a week', 
               'Once a week', 
               "Once a month",
               "Once a year",
               "Never"))
  }}) #??

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religion_importance", 
               label = "Importance of religion:",
               choices = c('Extremely important',
                           'Very important',
                           'Moderately important',
                           'Slightly important',
                           'Not at all important'))
  }})

renderUI({
  if (input$model_choice %in% c("social_views", "public_political_social", 'public_political_social_charity', 'public_political_social_charity_demo')) {
     selectInput("religion", 
               label = "Religion:",
               choices = c('Catholic',
                           'Protestant',
                           'Christian Orthodox',
                           'Jewish',
                           'Muslim',
                           'Sikh',
                           'Hindu',
                           'Buddhist',
                           'Atheist',
                           'Other'))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("gender", 
               label = "Gender:",
               choices = c("Male",
                           "Female",
                           "Transgender",
                           "Prefer not to say",
                           "Other"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("marital_status", 
               label = "Marital Status:",
               choices = c("Married",
                           "Widowed",
                           "Divorced",
                           "Separated",
                           "Never married"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("education", 
               label = "Education:",
               choices = c("Less than high school",
                           "High school",
                           "Some college",
                           "2 year degree",
                           "4 year degree",
                           "Graduate degree",
                           "Doctorate"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("income", 
               label = "Income:",
               choices = c('Less than $10,000', 
                           '$10,000 to $19,999',
                           '$20,000 to $29,999',
                           '$30,000 to $39,999',
                           '$40,000 to $49,999',
                           '$50,000 to $59,999',
                           '$60,000 to $69,999',
                           '$70,000 to $79,999',
                           '$80,000 to $89,999',
                           '$90,000 to $99,999',
                           '$100,000 to $149,999',
                           '$150,000 to $199,999',
                           '$200,000 to $299,999',
                           '$300,000 or more'))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("race", 
               label = "Race(s):",
               choices = c('White',
                           'Black or African American','American Indian or Alaska Native','Asian','Native Hawaiian or Pacific Islander', 'Other'), 
               multiple = TRUE)
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("education", 
               label = "Education:",
               choices = c("Less than high school",
                           "High school",
                           "Some college",
                           "2 year degree",
                           "4 year degree",
                           "Graduate degree",
                           "Doctorate"))
  }})

renderUI({
  if (input$model_choice %in% c("demographics", 'public_political_social_charity_demo')) {
     selectInput("age", 
               label = "Age:",
               choices = c('Under 18',
                           '18 - 24',
                           '25 - 34',
                           '35 - 44',
                           '45 - 54',
                           '55 - 64',
                           '65 - 74',
                           '75 - 84',
                           '85 or older'))
  }})

@@

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)
  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

@@

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
             geom_col() +
             labs(x="") + 
             #scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

@@

```{r}
renderValueBox({
  choice = df()
  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_noncentered[,2])),2)
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_noncentered[,2])),2)
  valueBox(gp_exp_util,
           color = "#3fad48")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_noncentered[,2])),2)
  valueBox(ox_exp_util,
           color = "#006633")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_noncentered[,2])),2)
  valueBox(rc_exp_util,
           color = "#660000")
})
```

@@

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)
